Numerical analysis of the influence of magnetic field waveforms on the performance of active magnetic regenerators \thanks{ An abridged version of this manuscript was presented at the ABCM International Congress of Mechanical Engineering (COBEM \colorbox{yellow}{Completar... cidade etc}). }

### 2019-11-05 PaperMagneticProfiles_JBSMSE.tex
Improved explanation of Type S valves.

The control of these blow durations can be achieved with the use of solenoid valves; a model for a digital hydraulic system and a calculation of valve power has been presented by  \cite{bib:cardoso16_trans}, who showed that, if the opening and closing times are fast enough compared to the cycle period, then valve power is indepedent of frequency and proportional to the blow duration.  An application of  electronic valves in AMR devices has been presented by \cite{bib:nakashima18-perfor-asses-solen-valves-flow}, using the control logic (for synchronizing the valve operation with the magnetic profile) described by \cite{bib:hoffmann17-actuat}.

@@

In the second approach, \emph{Type S} valves are used, with  nominal power lower in magnitude but which depends on frequency and blow fraction. For these valves, the valve power was experimentally correlated as:

@@

\colorbox{yellow}{A equacao acima precisa ser melhor contextualizada. Talvez os revisores pecam para dar uma descricao minima do experimento. Uma saida para nao ter que fazer isso seria revisar na introducao o trabalho nosso que mediu e propos a correlacao (foi o do Pedroca)  }

@@

\bibliography{thermo-ref/Thermo-Foam-Ref,thermo-ref/thesis}

>>>>

The control of these blow durations can be achieved with the use of solenoid valves; a model for a digital hydraulic system and a calculation of valve power has been presented by  \cite{bib:cardoso16_trans} and \cite{bib:cardoso18}.  An application of  electronic valves in AMR devices has been presented by \cite{bib:nakashima18-perfor-asses-solen-valves-flow}, using the control logic (for synchronizing the valve operation with the magnetic profile) described by \cite{bib:hoffmann17-actuat}.

@@

In the second approach, \emph{Type S} valves are used, with  nominal power lower in magnitude but which depends on frequency and blow fraction. These valves were experimentally characterized by \cite{bib:cardoso18}, where a single valve was attached to a measurement circuit and set to operate for varying values of blow fraction and frequency; the valve power was calculated from the averaged values of voltage and current after periodic steady state was reached. From these experiments, the valve power was experimentally correlated as:

@@

@@

\bibliography{thermo-ref/Thermo-Foam-Ref,thesis}
